Figures

### 2019-11-05 manuscript/figures.Rmd
minor changes, new paths

---
title: "Figures"
output: pdf_document
---

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
library(here)
opts_chunk$set(fig.width=12, fig.height=8, fig.path='figs/', fig.align= "center", echo=FALSE, warning=FALSE, message=FALSE)
```

```{r input, include=F}
field <- include_graphics(here("manuscript/figs/1_field/field.png"))
asvs <- include_graphics(here("manuscript/figs/2_taxonomy/combined.png"))
communities <- include_graphics(here("manuscript/figs/3_community/combined_fig_3.png"))
depth <- include_graphics(here("manuscript/figs/4_depth_comparison/depth_fig.png"))

field_cap <- "Representative photos and microphotos of snow algae. A. Red snow bloom above treeline, sample G1.1. B. Green snow hidden below surface, same sample site as S9. C. Bronze snow spots below trees. D. Red snow containing *Sanguina nivaloides* and *Chlainomonas rubra* morphologies. All scale bars 30 um. E. Orange-green snow containing *Chloromonas krienitzii* and *Chloromonas cf. nivalis*. F. Snow algae from green snow, including *Chloromonas cf. brevispina* and *Chlainomonas rubra*. G. Heatmap of cell count data, with samples on the y axis arranged from low to high elevation, and cell type on the x axis."

>>>>

---
title: "Figures"
output: bookdown::pdf_book
---

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
library(here)
opts_chunk$set(fig.path='figs/', fig.align= "center", echo=FALSE, warning=FALSE, message=FALSE)
```

```{r input, include=F}
field <- include_graphics(here("manuscript/figs/1_field/field2.png"))
asvs <- include_graphics(here("manuscript/figs/2_taxonomy/asvs_polished.png"))
communities <- include_graphics(here("manuscript/figs/3_community/combined_fig_3.png"))
depth <- include_graphics(here("manuscript/figs/4_depth_comparison/depth_fig.png"))

field_cap <- "Representative photos and microphotos of snow algae. A. Red snow bloom above treeline, sample G1.1. B. Green snow hidden below surface, same sample site as S9. C. Bronze snow spots below trees. D. Red snow containing \\emph{Sanguina nivaloides} (Sn) and //emph{Chlainomonas rubra} (Cr) morphologies. All scale bars 30 um. E. Orange-green snow containing \\emph{Chloromonas krienitzii} (Ck) and \\emph{Chloromonas cf. nivalis} (Cn). F. Snow algae from green snow, including \\emph{Chloromonas cf. brevispina} (Cb) and \\emph{Chlainomonas rubra} (Cr)."
